\section{Conclusion}

Forecasts used in operational decision-making are ultimately judged not by numerical accuracy
alone, but by their ability to support reliable execution under asymmetric cost. In many applied
settings, traditional symmetric accuracy metrics fail to capture the directional, temporal, and
economic structure of forecast error that determines operational success or failure. As a result,
forecasts that appear accurate by conventional measures may still impose unacceptable service
risk when deployed.

This paper introduced the \emph{Forecast Readiness Framework} (\FRF) as a structured approach
for evaluating forecast performance in such environments. By decomposing readiness into
complementary dimensions—service reliability, failure severity, tolerance stability, and economic
consequence—the framework provides a diagnostic lens that extends beyond aggregate accuracy.
Within this structure, Cost-Weighted Service Loss (\CWSL) serves as the economic axis, translating
directional forecast error into cost-aligned impact, while supporting diagnostics reveal how error
patterns affect execution.

The framework further incorporates a composite readiness signal, the \FRS, to support
deployment-level decisions, monitoring, and governance. Rather than collapsing evaluation into a
single loss function, the \FRF preserves interpretability while enabling principled trade-offs between
efficiency and reliability. Through an illustrative example, the paper demonstrated how forecasts
with comparable symmetric accuracy can exhibit sharply different readiness profiles, underscoring
the limitations of conventional evaluation practices.

By reframing forecast evaluation around readiness for deployment, the \FRF provides a practical
and generalizable basis for assessing forecasting systems in asymmetric operational contexts.
The framework is applicable across a wide range of short-horizon decision environments where
service reliability and cost asymmetry are central concerns. More broadly, it encourages a shift in
forecast evaluation from measuring how close predictions are to realized demand toward
understanding how forecast error shapes operational outcomes in practice.