% ==========================================================
% 060_governance_decision_artifact.tex
% Governance Decision Artifact
% ==========================================================

\section{The Governance Decision Artifact}
\label{sec:governance_decision_artifact}

The output of the Governance Decision Contract is a single, structured artifact:
the \texttt{GovernanceDecision}. This artifact is the sole authoritative
representation of governance intent within the Electric Barometer framework.
All downstream systems—evaluation, control, reporting, and automation—must
consume this artifact directly and must not infer or reconstruct governance
decisions independently.

The \texttt{GovernanceDecision} defines the \emph{compliance boundary} between
diagnostic evaluation and operational execution: once it is issued, no further
diagnostic reasoning or reinterpretation is admissible downstream.

This section defines the contents, semantics, and obligations associated with
the Governance Decision Artifact.

\subsection{Artifact Role and Authority}

The \texttt{GovernanceDecision} serves three simultaneous roles:

\begin{itemize}[leftmargin=*]
  \item \textbf{Interpretive authority:} it declares the admissible unit system
        and evaluation semantics.
  \item \textbf{Policy authority:} it determines whether readiness adjustment is
        allowed, constrained, or forbidden.
  \item \textbf{Audit record:} it provides an explicit, reviewable explanation
        for every governance outcome.
\end{itemize}

Together, these roles establish the artifact as a formal control object rather
than a mere interface. No downstream component is permitted to override,
reinterpret, or partially apply its contents. Governance authority exists only
at this boundary.

Figure~\ref{fig:governance_compliance_boundary} illustrates this role: the
\texttt{GovernanceDecision} defines a strict compliance boundary separating
diagnostic evaluation from operational execution.

\input{figures/governance_compliance_boundary}

\subsection{Required Fields}

A valid \texttt{GovernanceDecision} must contain the following fields:

\begin{itemize}[leftmargin=*]
  \item \textbf{Demand structure declaration}
        \begin{itemize}
          \item \DQC{} classification
          \item Detected grid unit $\Delta^{\ast}$ (if applicable)
        \end{itemize}

  \item \textbf{Authoritative evaluation space}
        \begin{itemize}
          \item Governing unit system (raw or snapped)
          \item Snapping requirement flag
        \end{itemize}

  \item \textbf{Compatibility determination}
        \begin{itemize}
          \item Authoritative \FPC{} classification
          \item Identification of admissible \FPC{} view (raw vs.\ snapped)
        \end{itemize}

  \item \textbf{Tolerance interpretation policy}
        \begin{itemize}
          \item Interpretation of $\tau$ (raw-unit or grid-unit)
          \item Validity constraints on tolerance magnitudes
        \end{itemize}

  \item \textbf{Readiness adjustment policy}
        \begin{itemize}
          \item Adjustment allowability
                (\textsc{Allowed}, \textsc{Conditional}, or \textsc{Disallowed})
          \item Applicable constraints or prerequisites
        \end{itemize}

  \item \textbf{Governance status indicator}
        \begin{itemize}
          \item Consolidated policy status (e.g.\ green / amber / red)
        \end{itemize}

  \item \textbf{Reasoning trace}
        \begin{itemize}
          \item Ordered, human-readable statements linking inputs to decisions
        \end{itemize}
\end{itemize}

All fields are mandatory. Partial or underspecified artifacts are invalid by
construction.

\subsection{Semantic Guarantees}

The Governance Decision Artifact provides the following guarantees:

\begin{itemize}[leftmargin=*]
  \item \textbf{Exclusivity:} exactly one unit system and one compatibility
        assessment govern interpretation.
  \item \textbf{Consistency:} tolerance semantics, diagnostics, and readiness
        policy are mutually coherent.
  \item \textbf{Determinism:} identical inputs and parameters yield identical
        artifacts.
  \item \textbf{Accountability:} every decision is attributable to declared
        diagnostics, thresholds, and governance rules.
\end{itemize}

These guarantees prevent ambiguous interpretation, policy drift, and silent
behavioral changes across the compliance boundary.

\subsection{Downstream Obligations}

Any system consuming a \texttt{GovernanceDecision} is obligated to:

\begin{itemize}[leftmargin=*]
  \item Apply evaluation and diagnostics only in the declared unit system,
  \item Enforce snapping requirements exactly as specified,
  \item Respect tolerance interpretation constraints,
  \item Enable readiness adjustment only when explicitly allowed,
  \item Surface governance status and reasoning when reporting outcomes.
\end{itemize}

Failure to comply with these obligations constitutes a governance violation,
not a modeling or implementation error.

\subsection{Why an Explicit Artifact}

Encoding governance outcomes as a structured artifact—rather than implicit
logic or scattered flags—serves a deliberate purpose. It ensures that
interpretation, policy, execution, and accountability converge at a single,
well-defined boundary.

The \texttt{GovernanceDecision} exists so that no system must guess:
\emph{what is allowed, how it should be interpreted, or why a decision was made}.
