\begin{abstract}
Forecast performance in operational environments is commonly evaluated using symmetric
accuracy metrics such as MAE, RMSE, and MAPE. These measures implicitly assume that
over-forecasting and under-forecasting impose equivalent cost, an assumption that rarely holds
in high-frequency systems where shortages generate substantially greater operational disruption
than excess. As a result, forecasts that appear accurate by traditional metrics may still fail to
support reliable execution.

We introduce the \emph{Forecast Readiness Framework} (FRF), a governed, multi-dimensional
approach for evaluating forecast performance under asymmetric error structures. Rather than
relying on a single loss function, the framework decomposes readiness into complementary
dimensions capturing service reliability, failure severity, tolerance stability, and economic
consequence. Within this framework, Cost-Weighted Service Loss (CWSL) serves as the primary
economic axis, explicitly quantifying asymmetric operational exposure, while supporting
diagnostics characterize how frequently shortfalls occur, how severe they are when they arise,
and whether forecast deviations remain within operationally absorbable bounds.

Crucially, FRF treats cost asymmetry and tolerance assumptions as governed evaluation
parameters rather than free modeling choices. Sensitivity analysis, calibration procedures, and
policy-based constraints are incorporated to ensure that readiness assessments are transparent,
auditable, and robust to uncertainty in operational cost structures. A composite readiness score
and optional adjustment layers support consistent deployment decisions without conflating
evaluation, calibration, and control.

By reframing forecast evaluation around readiness for deployment rather than numerical accuracy
alone, the Forecast Readiness Framework provides a structured basis for selecting, monitoring,
and governing forecasting systems in environments where service reliability and asymmetric
cost are central concerns. The framework is applicable across a range of operational domains,
including production planning, staffing, inventory management, logistics, and other
short-horizon decision systems.
\end{abstract}
