\section{Composite Readiness and Deployment Decisions}

The diagnostic components of the \FRF\ provide complementary perspectives on forecast error,
but operational deployment decisions often require a single, interpretable signal that summarizes
overall readiness. Practitioners must determine whether a forecast is sufficiently reliable to
support execution, compare competing models, and monitor changes in readiness over time.
Relying on individual diagnostics in isolation can obscure trade-offs among reliability, severity,
stability, and economic consequence. For this reason, the \FRF\ includes a composite measure,
the \emph{Forecast Readiness Score} (\FRS), designed to support deployment-level decisions.

The \FRS\ synthesizes information from the diagnostic components of the framework, anchoring
the composite on the economic axis provided by \CWSL\ while incorporating complementary
signals of service reliability and failure behavior. Conceptually, the \FRS\ reflects the extent to
which a forecast both limits cost-weighted operational loss and avoids readiness-critical failure
modes. In this sense, the \FRS\ does not replace individual diagnostics; rather, it aggregates them
in a manner that preserves their operational interpretation.

A defining characteristic of the \FRS\ is its asymmetry. Because \CWSL\ already encodes the
directional cost of forecast error, the composite score inherits sensitivity to under-forecasting
risk. Reliability-related diagnostics such as \NSL\ and severity-related measures such as \UD\
further modulate the score by penalizing forecasts that achieve low cost-weighted loss only by
concentrating risk in infrequent but severe shortfalls. Stability relative to tolerance, as captured
by \HRtau, ensures that forecasts whose deviations are frequently absorbed by the operational
system are distinguished from those that require frequent intervention.

The \FRS\ is intended to be interpreted as a readiness indicator rather than a loss function to be
minimized. Higher values correspond to forecasts that are more consistently aligned with
operational requirements under the specified asymmetry assumptions. Because the \FRS\
combines multiple diagnostics, its value should be interpreted in conjunction with the underlying
components when diagnosing failure modes or guiding model improvement. A change in the
\FRS\ may reflect deterioration in service reliability, increased failure severity, reduced tolerance
stability, or a shift in the economic alignment of forecast error.

The construction of the \FRS\ admits a formal specification that synthesizes the diagnostic
components of the framework while preserving their operational interpretation. In governance settings,
the score can be used to define acceptance thresholds, trigger review or retraining processes,
and communicate readiness to stakeholders who require a concise but meaningful summary of
forecast performance. By embedding economic consequence within a broader diagnostic
structure, the \FRS\ enables decision-makers to balance service reliability and efficiency in a
principled and transparent manner.