\section{Implications for Forecast Evaluation and Governance}

The \FRF\ has several implications for how forecasts are evaluated, selected, and governed in
operational environments characterized by asymmetric error cost. By shifting the focus from
numerical accuracy to readiness for deployment, the framework reframes forecast evaluation as
an operational risk management problem rather than a purely statistical exercise.

\subsection{Implications for Model Evaluation and Selection}

Traditional model evaluation procedures often rely on a small set of symmetric accuracy metrics
to compare competing forecasting approaches. Within the \FRF, such comparisons are
necessarily incomplete. Forecasts that perform similarly under symmetric metrics may differ
substantially in their service reliability, failure severity, or tolerance stability, leading to
materially different operational outcomes.

Evaluating models under the \FRF\ encourages practitioners to examine error structure explicitly.
Rather than selecting models based solely on aggregate accuracy, decision-makers can assess
whether a forecast’s deviations align with operational priorities, such as avoiding deep shortfalls
or maintaining stability within tolerance bounds. This perspective supports more informed trade-offs
between efficiency and reliability, particularly in environments where under-forecasting risk
dominates.

\subsection{Implications for Monitoring and Change Detection}

Because the diagnostic components of the \FRF\ isolate distinct failure modes, the framework
naturally supports ongoing monitoring of deployed forecasting systems. Changes in readiness
may arise from increased frequency of shortfalls, greater failure severity, reduced tolerance
stability, or shifts in the economic alignment of forecast error. Monitoring these dimensions
separately enables earlier detection of degradation than aggregate accuracy metrics alone.

At the composite level, trends in the \FRS\ can serve as a concise indicator of deployment
suitability over time. However, interpretation of changes in the composite score should be
informed by the underlying diagnostics. A declining \FRS\ may reflect different operational risks
depending on whether it is driven by reliability, severity, stability, or cost-weighted loss, each of
which may warrant a distinct response.

\subsection{Implications for Governance and Decision Support}

In organizational settings, forecast evaluation often plays a role in governance processes such as
model approval, retraining, and escalation. The \FRF\ provides a structured basis for defining
readiness criteria that are transparent and aligned with operational objectives. Acceptance
thresholds may be specified for individual diagnostics or for the \FRS, enabling consistent and
defensible deployment decisions across teams or business units.

By embedding asymmetric cost considerations explicitly, the framework also facilitates clearer
communication between technical and operational stakeholders. Rather than debating abstract
accuracy improvements, discussions can focus on service reliability, exposure to shortage risk,
and economic consequence. This alignment supports more effective decision support and reduces
the likelihood that technically sound forecasts are deployed in contexts for which they are not
operationally suited.

\subsection{Implications for Forecast Design and Use}

Finally, the \FRF\ has implications for how forecasts are designed and used. Awareness of readiness
criteria may influence modeling choices, encouraging approaches that trade marginal gains in
average accuracy for improvements in reliability or stability. At the same time, the framework
clarifies that no single diagnostic is universally dominant; readiness depends on the interaction
between error structure and operational context.

By treating readiness as a multi-dimensional construct, the \FRF\ encourages forecasting
practices that are explicitly aligned with execution requirements. This perspective supports more
robust deployment decisions in asymmetric environments, where the consequences of forecast
error are unevenly distributed and operational failure is costly.